Commutative character sheaves and geometric types for supercuspidal representations

### 2019-07-02 Geometric types.tex
Updates to the bibliography

This method of geometrization also applies to the example considered above.
Let $G = \SL_2$ over $\FFF$ and let $\chi : G(k) \to \mu_3 \subset \EEx$ be a non-trivial character.
In this case, $\tilde{\chi}= \chi^{-1}$. 
Since $G$ is connected and $\tilde{\chi}$ is a character, Proposition~\ref{prop:chitilde} produces a local system $\cs{L}$ on $G$ which geometrizes $\chi$.
This $\cs{L}$ is not conjugation-equivariant.

@@

\bib{bertapelle-gonzales:Greenberg}{unpublished}{
      author={Bertapelle, Alessandra},
      author={{Gonz\'ales-Avil\'es}, Cristian~D.},
       title={{The Greenberg functor revisited}},
        date={2016},
         url={http://arxiv.org/abs/1311.0051},
        note={\href{http://arxiv.org/abs/1311.0051}{arXiv:1311.0051
  [math.NT]}},
}

@@

\bib{cunningham-roe:13a}{article}{
author={Cunningham, Clifton},
author={Roe, David},
title={From the function-sheaf dictionary to quasicharacters of $p$-adic tori},
journal = {Journal of the Institute of Mathematics of Jussieu},
volume = {FirstView},
number = {6},
%month = {6},
year = {2016},
issn = {1475-3030},
pages = {1--37},
%numpages = {37},
doi = {10.1017/S1474748015000286},
URL = {http://journals.cambridge.org/article_S1474748015000286},
}

>>>>

This method of geometrization also applies to the example considered above.
Let $G = \SL_2$ over $\FFF$ and let $\chi : G(k) \to \mu_3 \subset \EEx$ be a non-trivial character.
In this case, $\tilde{\chi}= \chi^{-1}$. 
Since $G$ is connected and $\tilde{\chi}$ is a character, Proposition~\ref{prop:chitilde} produces a local system $\cs{L}$ on $G$ which geometrizes $\chi$.
This $\cs{L}$ is not conjugation-equivariant

@@

\bib{bertapelle-gonzales:Greenberg}{article}{
   author={Bertapelle, Alessandra},
   author={Gonz\'{a}lez-Avil\'{e}s, Cristian D.},
   title={The Greenberg functor revisited},
   journal={Eur. J. Math.},
   volume={4},
   date={2018},
   number={4},
   pages={1340--1389},
   issn={2199-675X},
%   review={\MR{3866700}},
 %  doi={10.1007/s40879-017-0210-0},
}

@@

\bib{cunningham-roe:13a}{article}{
   author={Cunningham, Clifton},
   author={Roe, David},
   title={From the function-sheaf dictionary to quasicharacters of $p$-adic
   tori},
   journal={J. Inst. Math. Jussieu},
   volume={17},
   date={2018},
   number={1},
   pages={1--37},
   issn={1474-7480},
%   review={\MR{3742553}},
%   doi={10.1017/S1474748015000286},
}
